On the instability and degeneracy of deep learning models

### 2017-11-07 writing/paper-note/docs/note_blinded.tex
Vardeman's edits, submitted to tech

\bigskip
\bigskip
\bigskip
%\begin{center}
  %{\LARGE\bf Title}
  \title{\bf A note on the instability and degeneracy of deep learning models}
%\end{center}
\medskip

@@

Due to their extreme sensitivity in probability structure, S-instability
in FOES models may often translate to numerical complications, and in
fact obstructions, in both simulation and statistical inference based on
likelihoods. We describe these aspects in Sections
\ref{mcmc}-\ref{bayes} with regard to data simulation, maximum
likelihood estimation and Bayes inference, respectively.

@@

Suppose one aims to apply MCMC to simulate data
\(\boldsymbol X=(X_1,\ldots,X_n)\) from a FOES model
\(P_{\boldsymbol \theta_N}(\boldsymbol x)\),
\(\boldsymbol x \in\mathcal{X}^N\) whereby a chain is constructed with
\(P_{\boldsymbol \theta_N}\) as the stationary distribution. For an
unstable FOES model, one component changes in outcomes may produce
radically different probabilities, which may then impose numerical
barriers to MCMC. For example, consider implementation of a Gibbs
sampler from the full conditional distributions
\(P_{\boldsymbol \theta_N} (X_i = x| \boldsymbol x_{-i})\),
\(x\in\mathcal{X}\), of each variable \(X_i\) based on values
\(\boldsymbol x_{-i}\in \mathcal{X}^{N-1}\) for the remaining variables,
say \(\boldsymbol X_{-i}\), in \(\boldsymbol X\). If a single change in
\(X_i\) from one value \(x_1\) to another \(x_2\) may produce two
outcomes \(\boldsymbol x^{(1)}\) and \(\boldsymbol x^{(2)}\) for
\(\boldsymbol X\) with vastly different probabilities under the joint
distribution \(P_{\boldsymbol \theta_N}\), then the Gibbs sampler can
have extreme log-ratios in its transition probabilities, \[
\log \left| \frac{P_{\boldsymbol \theta_N} (X_i =x_1 | \boldsymbol x^{(1)}_{-i})}{P_{\boldsymbol \theta_N} (X_i = x_2| \boldsymbol x^{(2)}_{-i}) } \right|=\log \left| \frac{P_{\boldsymbol \theta_N} ( \boldsymbol x^{(1)} )}{P_{\boldsymbol \theta_N} (  \boldsymbol x^{(2)} ) } \right|,
\]\\
as conditional probabilities are proportional to joint probabilities
that, with unstable models, can have unbounded log-probability ratios in
one-component changes (Theorem \ref{thm:instab-elpr}). This can hinder
the ability of chain to effectively explore the sample space of the
observations \(\boldsymbol X\), as the chain may mix poorly by moving
rapidly to, and slowly away from, sections of the sample space. In this
case, for example, the Markov chain may become entrapped within a mode
of the probability function, with rare chance of escaping to adequately
mimic the occupation frequencies in the overall sample space. If modes
of the unstable model are not unique, then important outcomes may be
missed without multiple chains or impractically enormous numbers of MCMC
samples. This mixing problem is due to the unstable stationary
distribution (unbounded ratios of probabilities under the joint model),
rather than in any particulars of the MCMC algorithm, and similar
complications can also arise for Metropolis-Hastings algorithms for
MCMC. Hence, while an unstable FOES model \(P_{\boldsymbol \theta_N}\)
may be valid and technically open to simulation by MCMC, the aspect of
instability can render applications of MCMC as numerically infeasible
for simulation purposes. This result is in line with conclusions of
Handcock (\protect\hyperlink{ref-handcock2003assessing}{2003}) and
Schweinberger
(\protect\hyperlink{ref-schweinberger2011instability}{2011}) for other
exponential models.

@@

Theorem \ref{thm:something} entails log-likelihood functions based on
unstable models are both inversely related and degenerate at opposited
signed parameters \(\boldsymbol \theta_N\) or \(-\boldsymbol \theta_N\),
so that likelihoods are highest at different extremes in data
configuration (e.g., \(\boldsymbol{x}_{\max, \boldsymbol \theta_N}\)
under \(\boldsymbol \theta\)-probabilities or
\(\boldsymbol{x}_{\min, \boldsymbol \theta_N}\) under
\(-\boldsymbol \theta\)-probabilities). If the observed outcome
\(\boldsymbol x\) for data \(\boldsymbol X\) is not a mode/anti-mode,
then probabilities for the outcome may be small under both parameters
\(\boldsymbol \theta_N\) and \(-\boldsymbol \theta_N\), in which case
associated optimization steps may then shift around zero and struggle to
converge. In many model formulations, the zero parameter
\(\boldsymbol \theta_N=\boldsymbol 0\) is a ``safe'' position among
parameters, representing a guaranteed stable model (having uniform
probabilities among outcomes), which can also tether a broad parameter
search attempted among unstable models. Handcock
(\protect\hyperlink{ref-handcock2003assessing}{2003}) describes similar
results for degenerate exponential models, and Theorem
\ref{thm:something} also supports an important finding of Schweinberger
(\protect\hyperlink{ref-schweinberger2011instability}{2011} Corollary 1)
for one-parameter linear exponential models \eqref{eq:expo}. In the latter
case, the likelihood score function at \(\boldsymbol \theta_N\) is the
expected value
\(\mu(\boldsymbol \theta_N)\equiv \mathrm{E}_{\boldsymbol \theta_N} g(\boldsymbol X)\)
of the sufficient statistic \(g(\cdot)\), and optimization involves
solving \(\mu(\cdot)=g(\boldsymbol x)\) for an observed outcome
\(\boldsymbol x\). For unstable models in this exponential class,
Schweinberger
(\protect\hyperlink{ref-schweinberger2011instability}{2011} Corollary 1)
shows that \[
\lim_{N\to \infty}\frac{\mu(\boldsymbol \theta_N) -L_n}{U_n-L_N}= \left\{ \begin{array}{lcl}
1 && \text{for } \boldsymbol \theta_N>0,\\
0 && \text{for } \boldsymbol \theta_N<0, \end{array}\right.
\] where again \(U_N\) and \(L_N\) denote the maximum and minimum values
of the statistic \(g(\boldsymbol x)\),
\(\boldsymbol x\in\mathcal{X}^N\). As described by Schweinberger
(\protect\hyperlink{ref-schweinberger2011instability}{2011}), the
implication for maximum likelihood estimation is that, unless an
observed outcome \(\boldsymbol x\) falls at an extreme \(U_N, L_N\)
(i.e., modes/anti-modes), optimization steps in the parameter space can
iterate in relatively small increments around zero and fail to converge.
For unstable one-parameter exponential models, the maximum likelihood
results of Schweinberger
(\protect\hyperlink{ref-schweinberger2011instability}{2011}) turn out to
be a special case of Theorem \ref{thm:something} and the LREP expansion
\eqref{eq:UL} in this setting; namely, for an unstable model with
\(\boldsymbol \theta_N>0\), \[
\frac{1}{\REP(\boldsymbol \theta_N)} \log\left[ \frac{P_{\boldsymbol \theta_N }(\boldsymbol X) }{\displaystyle{\min_{\boldsymbol y\in\mathcal{X}^N}} P_{\boldsymbol \theta_N }(\boldsymbol y)}\right] = \frac{\boldsymbol g(\boldsymbol X) - L_N}{U_N-L_N}\;\;\stackrel{p, \mathrm{E}}{\longrightarrow}\;\; 1
\] holds as \(N\to \infty\) by Theorem \ref{thm:something}, while under
\(-\boldsymbol \theta_N<0\) \[
\frac{1}{\REP(-\boldsymbol \theta_N)} \log\left[ \frac{P_{-\boldsymbol \theta_N }(\boldsymbol X) }{\displaystyle{\min_{\boldsymbol y\in\mathcal{X}^N}} P_{-\boldsymbol \theta_N }(\boldsymbol y)}\right] = \frac{U_N -\boldsymbol g(\boldsymbol X)}{U_N-L_N} = 1 - \frac{\boldsymbol g(\boldsymbol X) - L_N}{U_N-L_N} \;\;\stackrel{p, \mathrm{E}}{\longrightarrow}\;\; 1.
\] Again, when all probability in unstable models may be pushed to
opposite extremes in the sample space, due to a combination of
degeneracy and parameter sign, numerical complications in likelihood
maximization may occur.

@@

The potential numerical difficulties with maximum likelihood with
unstable models, as described in the previous section, can naturally
carry over to Bayes inference. Considering that the degeneracy issues
related to unstable models can cause likelihoods can be flat (e.g., near
zero) for many parameters under a given data outcome and that sign
changes in parameters can shift tremendous probability to extreme and
opposite outcomes in the sample space (e.g., Corollary \ref{cor:sign},
Theorem \ref{thm:something}), then numerical complications may arise
with Bayes inference in sampling a posterior parameter space based on
MCMC. The potential challenges in chain mixing are similar to those
presented in Section \ref{mcmc}, though in chain movements through the
parameter space as opposed to the sample space in data generation. That
is, in the Bayes setting for sampling a posterior distribution for
\(\boldsymbol \theta_N\), a chain may unstable to effectively explore
the parameter space due partly to extreme and potentially unbounded
probability ratios from parameter sign changes, which represents a
parameter space analog to how one component changes in the sample space
may impact data simulation with unstable models. For example, if
\(\pi(\cdot)\) denotes a prior density for \(\boldsymbol \theta_N\) and
\(q(\cdot | \cdot)\) denotes a proposal distribution for use in a
Metropolis-Hastings (MH) sampler, then MH acceptance probability becomes
\[
\alpha\left(\boldsymbol \theta^{(1)} \mid \boldsymbol \theta^{(2)}\right)= \min\left\{1,
\frac{q(\boldsymbol \theta_N^{(2)} \mid \boldsymbol \theta_N^{(1)})}{q(\boldsymbol \theta_N^{(1)} \mid \boldsymbol \theta_N^{(2)})}
\frac{P_{\boldsymbol \theta_N^{(1)}} ( \boldsymbol x ) \pi(\boldsymbol \theta_N^{(1)}) }{P_{\boldsymbol \theta^{(2)}_N} (  \boldsymbol x) \pi(\boldsymbol \theta_N^{(2)}) } \right\},
\] which indicates how parameter sensitivity in the likelihood
\(P_{\boldsymbol \theta_N} ( \boldsymbol x)\) may complicate sampling of
the posterior
\(P_{\boldsymbol \theta_N} ( \boldsymbol x) \pi(\boldsymbol \theta_N)\)
(i.e., moving from \(\boldsymbol \theta^{(1)}\) to
\(\boldsymbol \theta^{(2)}\) in the parameter space). Furthermore, the
potential for model instability and the size of the parameter space can
also become greater with the introduction of latent variables to
existing data variables, as involved in some model formulations
described in Sections \ref{rbm}-\ref{deep-learning}. As latent variables
are often sampled with parameters in a Bayes MCMC approach, this aspect
may further compound numerical problems in chain mixing.

>>>>

\bigskip
\bigskip
\bigskip
%\begin{center}
  %{\LARGE\bf Title}
  \title{\bf On the instability and degeneracy of deep learning models}
%\end{center}
\medskip

@@

Due to their induced sensitivity in probability structure, S-instability
in FOES models may often translate to numerical complications, and in
fact obstructions, in both simulation and statistical inference based on
likelihoods. We describe these aspects in Sections
\ref{mcmc}-\ref{bayes} with regard to data simulation, maximum
likelihood estimation and Bayes inference, respectively.

@@

Suppose one aims to apply MCMC to simulate data
\(\boldsymbol X=(X_1,\ldots,X_n)\) from a FOES model
\(P_{\boldsymbol \theta_N}(\boldsymbol x)\),
\(\boldsymbol x \in\mathcal{X}^N\) whereby a chain is constructed with
\(P_{\boldsymbol \theta_N}\) as the stationary distribution. For an
unstable FOES model, one-component changes in outcomes may produce
radically different probabilities, which may then impose numerical
barriers to MCMC. For example, consider implementation of a Gibbs
sampler from the full conditional distributions
\(P_{\boldsymbol \theta_N} (X_i = x| \boldsymbol x_{-i})\),
\(x\in\mathcal{X}\), of each variable \(X_i\) based on values
\(\boldsymbol x_{-i}\in \mathcal{X}^{N-1}\) for the remaining variables,
say \(\boldsymbol X_{-i}\), in \(\boldsymbol X\). If a single change in
\(X_i\) from one value \(x_1\) to another \(x_2\) may produce two
outcomes \(\boldsymbol x^{(1)}\) and \(\boldsymbol x^{(2)}\) for
\(\boldsymbol X\) with vastly different probabilities under the joint
distribution \(P_{\boldsymbol \theta_N}\), then the Gibbs sampler can
have extreme log-ratios in its transition probabilities, \[
\log \left| \frac{P_{\boldsymbol \theta_N} (X_i =x_1 | \boldsymbol x^{(1)}_{-i})}{P_{\boldsymbol \theta_N} (X_i = x_2| \boldsymbol x^{(2)}_{-i}) } \right|=\log \left| \frac{P_{\boldsymbol \theta_N} ( \boldsymbol x^{(1)} )}{P_{\boldsymbol \theta_N} (  \boldsymbol x^{(2)} ) } \right|,
\]\\
as conditional probabilities are proportional to joint probabilities
that, with unstable models, can have unbounded log-probability ratios in
one-component changes (Theorem \ref{thm:instab-elpr}). This can hinder
the ability of a chain to effectively explore the sample space of the
observations \(\boldsymbol X\), as the chain may mix poorly by moving
rapidly to, and slowly away from, sections of the sample space. In this
case, for example, the Markov chain may become entrapped within a mode
of the probability function, with rare chance of escaping to adequately
mimic the occupation frequencies in the overall sample space. If modes
of the unstable model are not unique, then important outcomes may be
missed without multiple chains or impractically enormous numbers of MCMC
samples. This mixing problem is due to the unstable stationary
distribution (unbounded ratios of probabilities under the joint model),
rather than in any particulars of the MCMC algorithm, and similar
complications can also arise for Metropolis-Hastings algorithms for
MCMC. Hence, while an unstable FOES model \(P_{\boldsymbol \theta_N}\)
may be valid and technically open to simulation by MCMC, the aspect of
instability can render applications of MCMC as numerically infeasible
for simulation purposes. This result is in line with conclusions of
Handcock (\protect\hyperlink{ref-handcock2003assessing}{2003}) and
Schweinberger
(\protect\hyperlink{ref-schweinberger2011instability}{2011}) for other
exponential models.

@@

Theorem \ref{thm:something} entails log-likelihood functions based on
unstable models are both inversely related and degenerate at opposited
signed parameters \(\boldsymbol \theta_N\) or \(-\boldsymbol \theta_N\),
so that likelihoods are highest at different extremes in data
configuration (e.g., \(\boldsymbol{x}_{\max, \boldsymbol \theta_N}\)
under \(\boldsymbol \theta\)-probabilities or
\(\boldsymbol{x}_{\min, \boldsymbol \theta_N}\) under
\(-\boldsymbol \theta\)-probabilities). If the observed outcome
\(\boldsymbol x\) for data \(\boldsymbol X\) is not a mode/anti-mode,
then probabilities for the outcome may be small under both parameters
\(\boldsymbol \theta_N\) and \(-\boldsymbol \theta_N\), in which case
associated optimization steps may then shift around zero and struggle to
converge.

In many model formulations, the zero parameter
\(\boldsymbol \theta_N=\boldsymbol 0\) is a ``safe'' position among
parameters, representing a guaranteed stable model (having uniform
probabilities among outcomes), which can also tether a broad parameter
search attempted among unstable models. Handcock
(\protect\hyperlink{ref-handcock2003assessing}{2003}) describes similar
results for degenerate exponential models, and Theorem
\ref{thm:something} also supports an important finding of Schweinberger
(\protect\hyperlink{ref-schweinberger2011instability}{2011} Corollary 1)
for one-parameter linear exponential models \eqref{eq:expo}. In the latter
case, the likelihood score function at \(\boldsymbol \theta_N\) is the
expected value
\(\mu(\boldsymbol \theta_N)\equiv \mathrm{E}_{\boldsymbol \theta_N} g(\boldsymbol X)\)
of the sufficient statistic \(g(\cdot)\), and optimization involves
solving \(\mu(\cdot)=g(\boldsymbol x)\) for an observed outcome
\(\boldsymbol x\). For unstable models in this exponential class,
Schweinberger
(\protect\hyperlink{ref-schweinberger2011instability}{2011} Corollary 1)
shows that \[
\lim_{N\to \infty}\frac{\mu(\boldsymbol \theta_N) -L_n}{U_n-L_N}= \left\{ \begin{array}{lcl}
1 && \text{for } \boldsymbol \theta_N>0,\\
0 && \text{for } \boldsymbol \theta_N<0, \end{array}\right.
\] where again \(U_N\) and \(L_N\) denote the maximum and minimum values
of the statistic \(g(\boldsymbol x)\),
\(\boldsymbol x\in\mathcal{X}^N\). As described by Schweinberger
(\protect\hyperlink{ref-schweinberger2011instability}{2011}), the
implication for maximum likelihood estimation is that, unless an
observed outcome \(\boldsymbol x\) falls at an extreme \(U_N, L_N\)
(i.e., modes/anti-modes), optimization steps in the parameter space can
iterate in relatively small increments around zero and fail to converge.
For unstable one-parameter exponential models, the maximum likelihood
results of Schweinberger
(\protect\hyperlink{ref-schweinberger2011instability}{2011}) turn out to
be a special case of Theorem \ref{thm:something} and the LREP expansion
\eqref{eq:UL} in this setting; namely, for an unstable model with
\(\boldsymbol \theta_N>0\), \[
\frac{1}{\REP(\boldsymbol \theta_N)} \log\left[ \frac{P_{\boldsymbol \theta_N }(\boldsymbol X) }{\displaystyle{\min_{\boldsymbol y\in\mathcal{X}^N}} P_{\boldsymbol \theta_N }(\boldsymbol y)}\right] = \frac{\boldsymbol g(\boldsymbol X) - L_N}{U_N-L_N}\;\;\stackrel{p, \mathrm{E}}{\longrightarrow}\;\; 1
\] holds as \(N\to \infty\) by Theorem \ref{thm:something}, while under
\(-\boldsymbol \theta_N<0\) \[
\frac{1}{\REP(-\boldsymbol \theta_N)} \log\left[ \frac{P_{-\boldsymbol \theta_N }(\boldsymbol X) }{\displaystyle{\min_{\boldsymbol y\in\mathcal{X}^N}} P_{-\boldsymbol \theta_N }(\boldsymbol y)}\right] = \frac{U_N -\boldsymbol g(\boldsymbol X)}{U_N-L_N} = 1 - \frac{\boldsymbol g(\boldsymbol X) - L_N}{U_N-L_N} \;\;\stackrel{p, \mathrm{E}}{\longrightarrow}\;\; 1.
\] Again, when all probability in unstable models may be pushed to
opposite extremes in the sample space, due to a combination of
degeneracy and parameter sign, numerical complications in likelihood
maximization may occur.

@@

The potential numerical difficulties with maximum likelihood with
unstable models, as described in the previous section, can naturally
carry over to Bayes inference. Considering that the degeneracy issues
related to unstable models can cause likelihoods can be flat (e.g., near
zero) for many parameters under a given data outcome and that sign
changes in parameters can shift tremendous probability to extreme and
opposite outcomes in the sample space (e.g., Corollary \ref{cor:sign},
Theorem \ref{thm:something}), then numerical complications may arise
with Bayes inference in sampling a posterior parameter space based on
MCMC. The potential challenges in chain mixing are similar to those
presented in Section \ref{mcmc}, though in chain movements through the
parameter space as opposed to the sample space in data generation. That
is, in the Bayes setting for sampling a posterior distribution for
\(\boldsymbol \theta_N\), a chain may unstable to effectively explore
the parameter space due partly to extreme and potentially unbounded
probability ratios from parameter sign changes, which represents a
parameter space analog to how one-component changes in the sample space
may impact data simulation with unstable models. For example, if
\(\pi(\cdot)\) denotes a prior density for \(\boldsymbol \theta_N\) and
\(q(\cdot | \cdot)\) denotes a proposal distribution for use in a
Metropolis-Hastings (MH) sampler, then MH acceptance probability becomes
\[
\alpha\left(\boldsymbol \theta^{(1)} \mid \boldsymbol \theta^{(2)}\right)= \min\left\{1,
\frac{q(\boldsymbol \theta_N^{(2)} \mid \boldsymbol \theta_N^{(1)})}{q(\boldsymbol \theta_N^{(1)} \mid \boldsymbol \theta_N^{(2)})}
\frac{P_{\boldsymbol \theta_N^{(1)}} ( \boldsymbol x ) \pi(\boldsymbol \theta_N^{(1)}) }{P_{\boldsymbol \theta^{(2)}_N} (  \boldsymbol x) \pi(\boldsymbol \theta_N^{(2)}) } \right\},
\] which indicates how parameter sensitivity in the likelihood
\(P_{\boldsymbol \theta_N} ( \boldsymbol x)\) may complicate sampling of
the posterior
\(P_{\boldsymbol \theta_N} ( \boldsymbol x) \pi(\boldsymbol \theta_N)\)
(i.e., moving from \(\boldsymbol \theta^{(1)}\) to
\(\boldsymbol \theta^{(2)}\) in the parameter space). Furthermore, the
potential for model instability and the size of the parameter space can
also become greater with the introduction of latent variables to
existing data variables, as involved in some model formulations
described in Sections \ref{rbm}-\ref{deep-learning}. As latent variables
are often sampled with parameters in a Bayes MCMC approach, this aspect
may further compound numerical problems in chain mixing.

### 2017-11-07 writing/paper-note/index.Rmd
Vardeman's edits, submitted to tech

---
title: "A note on the instability and degeneracy of deep learning models"
author: 
  - name: Andee Kaplan
    university: Iowa State University
    department: Department of Statistics
  - name: Daniel Nordman
    university: Iowa State University
    department: Department of Statistics
  - name: Stephen Vardeman
    university: Iowa State University
    department: |
      | Department of Statistics and Department of Industrial and
      | Manufacturing Systems Engineering
site: bookdown::bookdown_site
output: 
  bookdown::pdf_book:
    includes:
      in_header: ../resources/latex/header.tex
    toc: no
bibliography: [../resources/latex/refs_rbm.bib]
github-repo: andeek/rbm
abstract: |
  A probability model exhibits instability if small changes in a data outcome result in large, and often unanticipated, changes in probability. This instability is a property of the probability model, rather than the fitted parameter vector. For correlated data structures found in several application areas, there is increasing interest in predicting/identifying such sensitivity in model probability structure. We consider the problem of quantifying instability for general probability models defined on sequences of observations, where each sequence of length $N$ has a finite number of possible values. A sequence of probability models results, indexed by $N$, that accommodates data of expanding dimension. Model instability is formally shown to occur when a certain log-probability ratio under such models grows faster than $N$. In this case, a one component change in the data sequence can shift probability by orders of magnitude. Also, as instability becomes more extreme, the resulting probability models are shown to tend to degeneracy, placing all their probability on potentially small portions of the sample space. These results on instability apply to large classes of models commonly used in random graphs, network analysis, and machine learning contexts.
keywords: Degeneracy, Instability, Classification, Deep Learning, Graphical Models
blind: false
---

>>>>

---
title: "On the instability and degeneracy of deep learning models"
author: 
  - name: Andee Kaplan
    university: Iowa State University
    department: Department of Statistics
  - name: Daniel Nordman
    university: Iowa State University
    department: Department of Statistics
  - name: Stephen Vardeman
    university: Iowa State University
    department: |
      | Department of Statistics and Department of Industrial and
      | Manufacturing Systems Engineering
site: bookdown::bookdown_site
output: 
  bookdown::pdf_book:
    includes:
      in_header: ../resources/latex/header.tex
    toc: no
bibliography: [../resources/latex/refs_rbm.bib]
github-repo: andeek/rbm
abstract: |
  A probability model exhibits instability if small changes in a data outcome result in large, and often unanticipated, changes in probability. This instability is a property of the probability model, rather than the fitted parameter vector. For correlated data structures found in several application areas, there is increasing interest in predicting/identifying such sensitivity in model probability structure. We consider the problem of quantifying instability for general probability models defined on sequences of observations, where each sequence of length $N$ has a finite number of possible values. A sequence of probability models results, indexed by $N$, that accommodates data of expanding dimension. Model instability is formally shown to occur when a certain log-probability ratio under such models grows faster than $N$. In this case, a one component change in the data sequence can shift probability by orders of magnitude. Also, as instability becomes more extreme, the resulting probability models are shown to tend to degeneracy, placing all their probability on potentially small portions of the sample space. These results on instability apply to large classes of models commonly used in random graphs, network analysis, and machine learning contexts.
keywords: Degeneracy, Instability, Classification, Deep Learning, Graphical Models
blind: false
---
